Beam-Helicity and Beam-Charge Asymmetries \\ in the Bethe-Heitler and DVCS processes on \\ an Unpolarised Proton Target \underline{Paper Tag: PDVCS0607 (v1.0)} \underline{Drafting Committee: DC90 (\today)}

### 2011-05-31 results.tex
Adding comments from the first circulation

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs. \ref{release_bsa_0607} and \ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the imprecision of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

@@

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set are thus weighted towards the 2006-2007 result. This weighting towards the 2006-2007 result is not so evident for the beam helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest value of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude has no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must diminish in this $-t$ region due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The twist-3 $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude is compatible with zero, as is the twist-3 $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude, which is dependent on the squared DVCS term. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude are shown in the second row of Fig.~\ref{bsa_xbjrange}. Neither the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ nor the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ amplitude show any clear dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

@@

The solid and dashed curves in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from the colliders at H{\sc era} and H{\sc ermes} and Jefferson Lab. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically-motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A in Jefferson Laboratory; the model fit represented by the dashed curves includes this data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide calculations only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

The dash-dotted curves in Figs.~\ref{bsa_xbjrange} shows the result of a calculation made from a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD. The model incorporates fits to global deep-inelastic scattering and elastic data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from H{\sc ermes} and Jefferson Lab (to describe the skewness dependence). The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well, but the projections in the other kinematic variables are not as well described.

@@

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ dependence on any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in either of the distinct ranges of $x_{\textrm{B}}$. No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

>>>>

\section{Results}
Results for the beam-helicity and beam-charge asymmetry amplitudes extracted separately from previously published 1996-2005 and the new 2006-2007 hydrogen data sets, are presented in Figs. \ref{release_bsa_0607} and \ref{release_bca_0607}. Each of the asymmetry amplitudes is shown extracted in one bin over all kinematic variables (``overall'') and also projected against $-t$, $x_{\textrm{B}}$ and $Q^{2}$. All of the extracted asymmetry amplitudes are subject to a fractional contribution to the event yield from associated production (``Assoc. fraction''), which is shown in the bottom row of each figure. The beam-helicity asymmetry amplitudes are subject to an additional scale uncertainty from the measurement of the beam polarisation, which is stated in the captions of the figures.
\begin{figure}
\begin{center}
\includegraphics[width=15cm,keepaspectratio]{bsadvcsplots_eml_par13_bin6_release_pic_update_0607_9605}
  \caption{Beam-helicity asymmetry amplitudes extracted separately from
the 1996-2005 (open triangles) and 2006-2007 (filled squares)
hydrogen data. The inner error bars represent the statistical uncertainties, while total error bars denote the statistical and systematic uncertainties added in quadrature.  
An additional 2.8\,\% and 3.4\,\% scale uncertainty for the 1996-2005 and
2006-2007 data respectively is present in the amplitudes due to the \red{uncertainty} of
the beam polarisation measurement. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bsa_0607}
\end{center}
 \end{figure}

A statistical test was applied in order to check for possible incompatibility between the asymmetry amplitudes extracted from both data sets. Only the statistical uncertainties were employed in this test \red{as the largest contributions to the systematic uncertainties are largely correlated}. This test revealed no significant evidence for incompatibility between the data sets. The beam-helicity and beam-charge asymmetry amplitudes can therefore be extracted from the complete hydrogen data set recorded during the entire experimental operation of H{\sc ermes}.
\begin{figure}
\begin{center}
 \includegraphics[width=15cm,keepaspectratio]{bcaplots_eml_par13_bin6_release_pic_update_0607_9605_withassoc}
  \caption{Beam-charge asymmetry amplitudes extracted separately from the 1996-2005 (open triangles) and 2006-2007 (filled squares) hydrogen data.
The inner error bars represent the statistical uncertainties, while the total error bars denote the statistical and systematic uncertainties added in quadrature. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
 \label{release_bca_0607}
\end{center}
 \end{figure}

\begin{figure}
 \begin{center}
 \includegraphics[width=15cm]{bsadvcsplots_eml_par13_bin6_release_all_pic_update}
  \caption{The $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{LU,DVCS}}^{\sin\phi}$ and
$A_{\textrm{LU,I}}^{\sin(2\phi)}$ beam-helicity asymmetry amplitudes extracted from all the hydrogen data recorded at H{\sc ermes}
from 1996 until 2007. The error bars (bands) represent the statistical
(systematic) uncertainties. An additional 3.2\,\% scale uncertainty is present in the amplitudes due to the imprecision of
the beam polarisation measurement. Solid and dashed lines show model calculations from~\cite{Kum09}; calculations \red{from} Ref.~\cite{Liu11} are shown as dashed-dotted lines; amplitude values based on fits to data from Ref.~\cite{Gui11} are shown as open crosses. See text for details. The simulated fractional contribution from associated production to the yield in each kinematic bin is shown in the bottom row.}
  \label{bsa_xbjrange}
 \end{center}
\end{figure}

@@

The results of the beam-helicity and beam-charge asymmetry amplitudes extracted from the complete 1996-2007 hydrogen sample are shown in Figs.~\ref{bsa_xbjrange} and \ref{bca_xbjrange}. The number of analysable events available from the 2006-2007 data set (67815) is approximately three times greater than the number of events recorded in the 1996-2005 sample (24817). The  asymmetry amplitudes extracted from the complete 1996-2007 data set thus \red{resemble} the 2006-2007 result. This \red{resemblance} to the 2006-2007 result is not so evident for the beam\red{-}helicity asymmetry amplitudes because the beam polarisation was lower in 2006 and 2007.

The first and second harmonics of $\mathcal{A}_{\textrm{LU,I}}$, which are
sensitive to the interference term in the scattering amplitude, are shown in the first and third rows of Fig.~\ref{bsa_xbjrange}. The leading-twist amplitude $A_{\textrm{LU,I}}^{\sin\phi}$ has the largest \red{magnitude} of any of the amplitudes when extracted in a single bin from the entire data set. This amplitude \red{shows} no strong dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$, implying a strong dependence at smaller values of $-t$ as the amplitude must \red{approach zero as $-t$ approaches zero} due to the dependence of the amplitude on the factor $k$ from Eq.~\ref{eq:s1}. The $A_{\textrm{LU,I}}^{\sin\phi}$ amplitude is sensitive to the imaginary part of the CFF $\mathcal{H}$ and thereby can constrain GPD $\textit{H}$. The $A_{\textrm{LU,DVCS}}^{\sin\phi}$ \red{asymmetry is} shown in the second row of Fig.~\ref{bsa_xbjrange}. \red{Both the $A_{\textrm{LU,DVCS}}^{\sin\phi}$ amplitude and the $A_{\textrm{LU,I}}^{\sin(2\phi)}$ asymmetry are compatible with zero, and neither asymmetry shows} any dependence on $-t$, $x_{\textrm{B}}$ or $Q^{2}$. The systematic error bands associated with the asymmetry amplitudes extracted from the combined data set were determined using Monte Carlo simulations that reflect the equipment used in the various stages of the H{\sc ermes} experiment.

@@

\red{The curves in  Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} show the results of model calculations at the centere of the kinematic bins used for the data extractions.} The solid and dashed curves show calculations from a global fit of GPDs to experimental data~\cite{Kum09} including information from \red{H{\sc ermes} and Jefferson Laboratory,} and the collider \red{experiments} at H{\sc era}. The basic model is a minimalist dual representation of GPDs with only (very) weakly entangled skewness and $t$ dependences. In the model, the $t$ dependence is approximated by a physically motivated Regge dependence. The solid curves represent the model fit without data from experiments \cite{Cam06, Gir08} at Hall A \red{of} Jefferson Laboratory; the model fit represented by the dashed curves includes \red{these} data. Both fits include the 1996-2005 H{\sc ermes} data. The model incorporates only twist-2 GPDs and so can provide \red{results} only for the $A_{\textrm{LU,I}}^{\sin\phi}$, $A_{\textrm{C}}^{\cos(0\phi)}$ and $A_{\textrm{C}}^{\cos\phi}$ asymmetry amplitudes. All of the amplitudes are well described by the model.

The dash-dotted curves in Fig.~\ref{bsa_xbjrange} shows the result of a calculation \red{based on} a quark-diquark model with a Regge-inspired term that is included in order to describe accurately parton distribution functions at low $x$ values~\cite{Liu11}. The ``Regge'' term includes contributions that determine the $t$-dependence of the corresponding GPD. The model incorporates fits to global deep-inelastic and elastic \red{scattering} data (to account for the $\xi$-independent limits and moments of the underlying GPDs) and exclusive data from Jefferson \red{Laboratory} (to describe the skewness dependence). The model describes the $t$-projections of the $A^{\sin\phi}_{\textrm{LU}}$ amplitude well \red{in the H{\sc ermes} kinematic region}, but the projections in the other kinematic variables are not as well described.

@@

In order to provide more detailed information that can be used in future fits, in particular for the determination of the entanglement of the skewness and $-t$ dependences of GPDs, the amplitudes already presented in Figs.~\ref{bsa_xbjrange} and~\ref{bca_xbjrange} are shown as a function of $-t$ for three different ranges of $x_{\textrm{B}}$ in Figs.~\ref{bsa_xbjrange2} and~\ref{bca_xbjrange2}. There is no observed $-t$ dependence o\red{f} any of the $\mathcal{A}_{\textrm{LU}}$ amplitudes in \red{any} of the distinct ranges of $x_{\textrm{B}}$. No additional features or $-t$ dependences are observed for the $\mathcal{A}_{\textrm{C}}$ amplitudes in these separate $x_{\textrm{B}}$ ranges.

### 2011-05-31 summary.tex
Adding comments from the first circulation

Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. An analogous set of asymmetry amplitudes were extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}. A comparison of the amplitudes extracted from these independent data sets have shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The resulting beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. The result of this extraction of asymmetry amplitudes show that there is a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry. There are also non zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry. Each of the other higher order asymmetry amplitudes are consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$. No localised features are observed in any particular $t$-bin.

>>>>

Beam-helicity and beam-charge asymmetries in the azimuthal distribution of real photons from leptoproduction on an unpolarised hydrogen target have been presented. These asymmetries were extracted from a new unpolarised hydrogen data set taken during the 2006 and 2007 operating period of H{\sc ermes}. An analogous set of asymmetry amplitudes \red{was} extracted previously from hydrogen data obtained during the 1996-2005 experimental period as described in Ref.~\cite{Air09}. A comparison of the amplitudes extracted from these independent data sets \red{has} shown that they are compatible and the asymmetry amplitudes can therefore be extracted from the complete 1996-2007 event sample. The \red{extracted} asymmetry amplitudes show a strong signal in the first harmonic of the interference contribution to the beam-helicity asymmetry. The beam-charge asymmetry amplitudes represent the most statistically precise DVCS result that will be published by the H{\sc ermes} collaboration. There are non\red{-}zero amplitudes in the zeroth and first harmonics of the beam-charge asymmetry. Each of the higher order asymmetry amplitudes \red{is} consistent with zero. The combined results are compared to calculations from ongoing work to fit GPD models to experimental data. All data amplitudes are also presented as projections in $-t$ in bins of $x_{\textrm{B}}$. No \red{additional} features are observed in any particular $\red{x_{\textrm{B}}}$-bin.
